%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Harvey Mudd College} % Organization
    {Clay-Wolkins Fellowship Research Assistant} % Job title
    {Claremont, CA} % Location
    {May 2022 - Present} % Date(s)
    {
    \begin{cvitems}
      \item {
      Automated testing of processor functionality for OpenHWGroup's processor CVW-Wally using SystemVerilog testbenches and python.
      }
      \item{
      Modified existing scripts and testbenches to allow for easier testing of the Linux boot process.
      }
      \item {
      Worked on the AHBLite bus as well as peripheral tests for open source microprocessor CVW-Wally.
      }
      \item{
      Rebuilt AHBLite bus' finite-state machine to implement burst mode, resulting in a 2\% performance increase.
      }
      \item{
      Designed tests for a GPIO, PLIC, and UART in RISC-V Assembly and implemented them in SV testbenches to verify processor functionality.
      }
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Qualcomm} % Organization
    {Digital Design Intern} % Job title
    {Claremont, CA} % Location
    {Aug. 2023 - Present} % Date(s)
    {
    \begin{cvitems}
      \item{
      Worked with a team to analyze RTL projects to determine when a project will cause problems in logic synthesis.
      }
      \item{
      Wrote wrapper script to perform synthesis with Synopsys Design Compiler for RTL Projects to analyze synthesis performance.
      }
      \item{
      Synthesized projects using yosys to create AND-Inverter graphs in the AIGER format for analysis in Python.
      }
      \item{
      Used Python to analyze AND-Inverter Graphs for parameters identified to cause synthesis issues such as high logical effort.
      }
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Silvus Technologies} % Organization
    {R\&D Intern} % Job title
    {Westwood, CA} % Location
    {Jun. 2023 - Aug. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
        Characterized the frequency response of an embedded radio using an RF Testbench controlled via MATLAB using VISA commands
        }
        \item {
        Built a parser for Synopsys netlists using Python, speeding up detection of transistor issues and saving hundreds of hours of manual searching.
        }
        \item {
        Used existing codebase to automate phase calibration of multi-antenna high-speed embedded radios.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tesla} % Organization
    {Machine Learning Intern} % Job title
    {Claremont, CA} % Location
    {Jan. 2023 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
        Used Python to analyze a large dataset of manufacturing test failures to predict failure causes with 78\% accuracy
        }
        \item{
        Wrote Python scripts using RegEx to feature engineer an existing database into a csv for ML methods.
        }
        \item{
        Delivered framework for testing and training models based on Tesla's database
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
