%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Clay-Wolkins Fellowship VLSI Research} % Job title
    {Harvey Mudd College} % Organization
    {Claremont, CA} % Location
    {Mar. 2024 - Present} % Date(s)
    {
    \begin{cvitems}
      \item {
      Automated recurring design verification and performance verification for OpenHWGroup's processor CVW-Wally using Systemverilog testbenches and python.
      }
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Qualcomm VLSI Engineer} % Job title
    {Qualcomm through Harvey Mudd College} % Organization
    {Claremont, CA} % Location
    {Aug. 2024 - Present} % Date(s)
    {
    \begin{cvitems}
      \item{
      Worked with a team to analyze RTL projects to determine when a project will cause problems in logic synthesis.
      }
      \item{
      Wrote wrapper script to perform synthesis with Synopsys Design Compiler for RTL Projects to analyze synthesis performance.
      }
      \item{
      Synthesized projects using yosys to create AND-Inverter graphs in the AIGER format for analysis in Python.
      }
      \item{
      Used Python to analyze AND-Inverter Graphs for parameters identified to cause synthesis issues such as high logical effort.
      }
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {R\&D Intern} % Job title
    {Silvus Technologies} % Organization
    {Westwood, CA} % Location
    {Jun. 2024 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
        Characterized the frequency response of a complex embedded radio using an RF Testbench controlled via MATLAB using VISA commands to validate design
        }
        \item {
        Built a parser for DC Synopsys files using Python, speeding up detection of transistor issues, reducing the chance of signal skew in manufacturing.
        }
        \item {
        Used existing codebase to automate phase calibration of multi-antenna high-speed embedded radios.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Tesla ML Engineer} % Job title
    {Tesla through Harvey Mudd College} % Organization
    {Claremont, CA} % Location
    {Jan. 2023 - May 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
        Developed a Machine Learning algorithm using Python to analyze a large dataset of car test successes and failures to determine which connector is causing issues.
        }
        \item{
        Wrote Python scripts using REGEX to feature engineer an existing database into a csv for ML methods.
        }
        \item{
        Automated sweeps of different parameters for ML models to determine the best model for Tesla's dataset.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Clay-Wolkins Fellowship VLSI Research} % Job title
    {Harvey Mudd College} % Organization
    {Claremont, CA} % Location
    {May 2022 - Jul. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
        Worked on the AHBLite bus as well as peripheral tests for open source microprocessor CVW-Wally.
        }
        \item{
        Rebuilt AHBLite bus' finite-state machine to implement burst mode, resulting in a 2\% performance increase.
        }
        \item{
        Designed verification tests for GPIO, PLIC, and UART in RISC-V Assembly and implemented them to verify processor functionality using SystemVerilog testbenches.
        }
        \item{
        Handled daily design verification using existing infrastructure to ensure the processor would remain functional for testing.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
