%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
\name{Kaitlin}{Lucio}
\position{Electrical and Computer Engineer}

\mobile{(+1) 909-736-7148}
\email{kaitlin.verilog@gmail.com}
% \github{slmnemo}
\linkedin{kaitlinverilog}
%\dateofbirth{January 1st, 1970}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \hackerrank{hackerrank-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

% \quote{``Be the change that you want to see in the world."}

%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Application for Entry Level Electrical Engineer}
  {PAE}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Cover Letter}
% How the letter is opened
\letteropening{Dear PAE,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
% \letterenclosure[Attached]{}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Kaitlin Lucio --- Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

  \tab Hello, I am Kaitlin Lucio, an EIT-eligible electrical engineer with a degree in general engineering.
  % I am aware that this position is asking for electrical engineering degree holders, but my background
  % overlaps significantly with a typical electrical engineering degree.
  In the acquisition of my degree, I have taken coursework primarily for electronics such as control systems,
  solid state amplifiers, circuit analysis, and other electrical classes.
  As such, I possess the skills of any other electrical engineer.
  I am also actively pursuing my EIT ECE certification.
  PAE caught my interest as a firm focused on sustainable engineering in the
  Seattle area, as a major reason I want to pivot fields is specifically to create a more sustainable future.
  
  \tab In the past, I have worked as an electrical firmware engineer focused on FPGAs.
  I am seeking to switch industries to infrastructure-related work.
  The work described in the job listing is interesting to me because I want to work in a field
  where my work directly improves the lives of those around me.
  For me, working with and designing things that directly help people is enriching, and this
  is a core reason for the switch.
  In addition to emotional impact, I also want to be able to understand and work on electrical power infrastructure so that
  I can help build a greener US electrical system.

  \tab As a former silicon and aerospace engineer, I bring with me an attention to detail, a strong work ethic and
  many soft skills.
  I have worked on teams developing camera systems for satellites and a computer chip running Linux at previous
  positions where I learned the value of details and triple checking my work.
  As a result of working in these positions, I have also become highly proficient in working with
  computers, a skill that allows me to pick up new software very quickly.
  Within my duties of work, I have also had to
  conduct customer meetings, meet deadlines, and work in a team; skills which are transferrable to any industry.
  
  \tab In addition to my computer proficiency and attention to detail, I have a strong understanding of electrical
  systems.
  At my previous positions, I was involved in the design and testing of multiple electrical devices related to radios,
  custom cameras, and medical devices.
  These past projects have given me intuition into how electrical systems behave,
  such as how magnetic interference can cause sudden failure during operation, how power and heat
  dissipation affect components, and how loading can affect supply voltages.

  \tab I hope that I will be considered for this position at PAE, and I look forward to hearing back.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
